Transitivity of Subtyping for Intersection Types, Directly

### 2019-06-20 papers/intersection-transitivity.tex
check

\begin{figure}
  \begin{tabular}{ll}
    (refl$_α$) & $α <: α$ \\[2ex]
    (incl$_L$) & $\inference{A <: C}{A ∩ B <: C}$ \\[2ex]
    (incl$_R$) & $\inference{B <: C} A ∩ B <: C$ \\[2ex]
    (glb) & $\inference{C ≤ A & C ≤ B}{C ≤ A ∩ B}$ \\[2ex]
    ($\TOP_{\mathrm{top}}$) & $A <: \TOP$ \\[2ex]
    ($\TOP→$) & $\TOP <: A → \TOP$ \\[2ex]
    ($→$) &$\inference{D ⊆ C & A' <: \dom{D} & \cod{D} <: B' }{C <: A' → B'}$
  \end{tabular}
  \caption{New Subtyping Relation}
  \label{fig:new-subtyping}
\end{figure}

>>>>

\begin{figure}
  \begin{tabular}{ll}
    (refl$_α$) & $α <: α$ \\[2ex]
    (incl$_L$) & $\inference{A <: C}{A ∩ B <: C}$ \\[2ex]
    (incl$_R$) & $\inference{B <: C}{A ∩ B <: C}$ \\[2ex]
    (glb) & $\inference{C ≤ A & C ≤ B}{C ≤ A ∩ B}$ \\[2ex]
    ($\TOP_{\mathrm{top}}$) & $A <: \TOP$ \\[2ex]
    ($\TOP→$) & $\TOP <: A → \TOP$ \\[2ex]
    ($→'$) &$\inference{D ⊆ C & A' <: \dom{D} & \cod{D} <: B' }{C <: A' → B'}$
  \end{tabular}
  \caption{New Subtyping Relation}
  \label{fig:new-subtyping}
\end{figure}
